Innovations Report: Procedural Fur System

### 2018-03-17 docs/paper.tex
more on docs

>>>>

\subsubsection{Rendering} \label{sec:rendering}

By default, 'Mesh' and 'Curves' objects present in the node graph are not rendered in the viewport. For example, the user may want to distribute curves from hidden 'scalp' geometry, or use a set of hidden curves as clumping attractors. Therefore it was necessary to implement a pair of rendering nodes that would take a 'Mesh' or 'Curves' object as an input, and provide shading controls for rendering them in the viewport.

Whilst rendering and shading triangulated meshes is relatively straightforward, as described in \cite{objLoading}, there are multiple different approaches one could use to render curves. The technique I chose to implement relies on drawing an empty VAO multiple times, and using \texttt{gl\_PrimitiveIDIn} from within a geometry shader to determine which curve from the bound \texttt{GL\_SHADER\_STORAGE\_BUFFER} should be drawn. Figure~\ref\{} shows how this was achieved.

% I opted to make use of OpenGL's geometry shaders, drawing an empty VAO multiple times, and using \texttt{gl\_PrimitiveIDIn} from within a geometry shader to determine which curve from the bound \texttt{GL\_SHADER\_STORAGE\_BUFFER} should be drawn.
